Windowed least-squares model reduction for dynamical systems

### 2019-10-09 main.tex
latest

\section{Derivation of the Euler--Lagrange Equations}\label{appendix:eulerlagrange}
This section details the derivation of the Euler Lagrange equations. To this end, we consider the generic functional of the form,
\begin{equation}\label{eq:el_gen}
\mathcal{J}: (\statey,\stateyDot) \mapsto  \int_a^b \integrand(\statey(t),\stateyDot(t),t)  dt,
\end{equation}
where $\integrand: \RR{M} \times \RR{M} \times[a,b] \rightarrow  \RR{}$ (for arbitrary $M$) with $\integrand: (\stateyDiscrete,\stateyDotDiscrete,t) \mapsto \integrand(\stateyDiscrete,\stateyDotDiscrete,t)$. We now introduce the function $\statez: [a,b] \rightarrow \RR{M}$ that is implicitly defined as an extremum of~\eqref{eq:el_gen} subject to the boundary condition $\statez(a) = \statez_a$. 
We introduce an arbitrary function $\variation : [a,b] \rightarrow \RR{M}$ with the boundary condition $\variationArg{a} = \bz$ and define a variation from the extremal by,
\begin{align*}
\statezBar  &: (\tau,\delta) \mapsto \statez(\tau) + \delta \variation(\tau),\\
&: [a,b] \times \RR{} \rightarrow \RR{M}.
\end{align*}
We note that $\statezBar$ obeys the same boundary conditions as $\statez$ since $\variationArg{a} = \bz$.
We define a new function that is equivalent to~\eqref{eq:el_gen} evaluated at $\statezBar(t,\cdot)$,
$$
\mathcal{J}_{\delta}: \delta \mapsto \int_a^b \integrand(\statezBar(t,\delta),\statezDotBar(t,\delta) ,t)  dt.
$$

@@

We first evaluate the derivative. First using the chain rule,

@@

Noting that,

@@

we have,

@@

= \int_a^b \bigg[ \frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t;\epsilon),\statezDotBar(t;\epsilon),t \big) \variation(t)  + \frac{\partial \integrand}{\partial \stateyDotDiscrete } \big(\statezBar(t;\epsilon),\statezDotBar(t;\epsilon) ,t \big) \variationDot(t) \bigg]dt. $$

@@

\int_a^b \frac{d}{d\epsilon}\bigg[ \integrand \big(\statezBar(t;\epsilon),\statezDotBar(t;\epsilon),t \big) \bigg] dt =  \int_a^b  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t;\epsilon),\statezDotBar(t;\epsilon) , \big) \variation(t) - \frac{d}{dt}\bigg( \frac{\partial \integrand}{\partial \stateyDotDiscrete }  \big(\statezBar(t;\epsilon),\statezDotBar(t;\epsilon) ,t \big) \bigg) \variation(t) \bigg]dt + \\ \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statezBar(b;\epsilon),\statezDotBar(b;\epsilon) ,b \big) \variation(b) . 

@@

  \int_a^b  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t;\epsilon),\statezDotBar(t;\epsilon),t \big) \variation(t) - \frac{d}{dt}\bigg( \frac{\partial \integrand}{\partial \stateyDotDiscrete }  \big(\statezBar(t;\epsilon),\statezDotBar(t;\epsilon),t \big) \bigg) \variation(t) \bigg]dt + \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statezBar(b;\epsilon),\statezDotBar(b;\epsilon),b \big) \variation(b)  = 0. 

@@

\section{Evaluation of Gradients in the Euler--Lagrange Equations for \methodAcronym}\label{appendix:vector_calc} 
To obtain the specific form of the Euler--Lagrange equations for the \methodAcronym\ formulation, we need to evaluate the gradients in~\eqref{eq:el1} for the integrand,
\begin{align*}\label{eq:integrand_apx}
 \minintegrand & \vcentcolon
(\genstateyDiscreteArgnt{}, \genstateyDiscreteDotArgnt{} ,t) \mapsto \frac{1}{2} \big[
\basisspace \genstateyDiscreteDotArgnt{} - \velocity(\basisspace \genstateyDiscreteArgnt{}
+ \stateIntercept,t) \big]^T \stweightingMatArg{} \big[
\basisspace \genstateyDiscreteDotArgnt{}  - \velocity(\basisspace \genstateyDiscreteArgnt{} +
\stateIntercept,t) \big], \\ & 
\vcentcolon \RR{\romdim} \times \RR{\romdim} \times [0,T]
 \rightarrow \RR{} .  
\end{align*}
To evaluate the gradients, we first expand $\minintegrand$:
\begin{align*}
 \minintegrand(\genstateyDiscrete,\dot{\genstateyDiscrete},t)  &= \frac{1}{2} \big[ \basisspace \genstateyDiscreteDotArgnt{}  - \velocity(\basisspace \genstateyDiscreteArgnt{} + \stateIntercept,t) \big]^T \stweightingMatArg{n} \big[ \basisspace \genstateyDiscreteDotArgnt{} - \velocity(\veloargsromy) \big] \\ 
 &= \frac{1}{2}\big[\basisspace \genstateyDiscreteDotArgnt{}  \big]^T  \stweightingMatArg{n}  \big[\basisspace \genstateyDiscreteDotArgnt{} \big]  - \frac{1}{2}\big[ \velocity(\veloargsromy) \big]^T \stweightingMatArg{n}  \big[\basisspace \genstateyDiscreteDotArgnt{}\big] - \frac{1}{2} \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{n} \big[ \velocity(\veloargsromy) \big]  \\ &+ \frac{1}{2}\big[\velocity(\veloargsromy) \big]^T \stweightingMatArg{n} \big[ \velocity(\veloargsromy) \big].
\end{align*}
Since $\stweightingMat$ is symmetric,
\begin{equation}\label{eq:int_expand}
 \minintegrand(\genstateyDiscrete,\genstateyDiscreteDot,t)  = \frac{1}{2}\big[\basisspace \genstateyDiscreteDotArgnt{}  \big]^T  \stweightingMatArg{n}  \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]  -  \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{n} \big[ \velocity(\veloargsromy) \big]  + \frac{1}{2}\big[\velocity(\veloargsromy) \big]^T \stweightingMatArg{n} \big[ \velocity(\veloargsromy) \big].
\end{equation}
For notational purposes, we write the above as,
$$  \minintegrand(\genstateyDiscrete,\dot{\genstateyDiscrete},t) =  \minintegrand_1(\genstateyDiscrete,\genstateyDiscreteDot,t) +  \minintegrand_2(\genstateyDiscrete,\genstateyDiscreteDot,t) +  \minintegrand_3(\genstateyDiscrete,\genstateyDiscreteDot,t),$$
where
\begin{align*}
&\minintegrand_1(\genstateyDiscrete,\genstateyDiscreteDot,t) \equiv  \frac{1}{2}\big[\basisspace \genstateyDiscreteDotArgnt{}  \big]^T  \stweightingMatArg{n}  \big[ \basisspace \genstateyDiscreteDotArgnt{} \big], \\
&   \minintegrand_2(\genstateyDiscrete,\genstateyDiscreteDot,t) \equiv   -  \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{n} \big[ \velocity(\veloargsromy) \big], \\
&  \minintegrand_3(\genstateyDiscrete,\genstateyDiscreteDot,t) \equiv  \frac{1}{2}\big[\velocity(\veloargsromy) \big]^T \stweightingMatArg{n} \big[ \velocity(\veloargsromy) \big] . 
\end{align*}
Constructing the Euler--Lagrange equations for this functional $\minintegrand$ requires evaluating the derivatives $\frac{\partial \minintegrand}{\partial \genstateyDiscrete}$ and $\frac{\partial \minintegrand}{\partial \genstateyDiscreteDot}$. We start by evaluating $\frac{\partial \minintegrand}{\partial \genstateyDiscrete}$ and go term by term.

@@

\frac{\partial \minintegrand_2}{\partial \genstateyDiscrete}  &= -\frac{\partial}{\partial \genstateyDiscrete} \bigg( \big[ \basisspace \genstateyDiscreteDot \big]^T \stweightingMatArg{n} \big[ \velocity(\veloargsromy) \big] \bigg) \\ 
&= - \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{n} \frac{\partial}{\partial \genstateyDiscreteArgnt{}} \bigg( \big[ \velocity(\veloargsromy) \big]  \bigg)\\
 &= -\big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{n}   \frac{\partial \velocity}{\partial \stateyDiscrete}\frac{\partial \stateyDiscrete}{\partial \genstateyDiscrete} \\
& = - \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{n}  \frac{\partial \velocity}{\partial \stateyDiscrete}\basisspace \\
&= -[\genstateyDiscreteDotArgnt{}]^T \basisspace^T \stweightingMatArg{n} \frac{\partial \velocity}{\partial \stateyDiscrete}  \basisspace.

@@

\frac{\partial  \minintegrand_3}{\partial \genstateyDiscrete}  &= \frac{1}{2} \frac{\partial }{\partial \genstateyDiscrete} \bigg( \big[\velocity(\veloargsromy) \big]^T \stweightingMatArg{n}\big[ \velocity(\veloargsromy) \big] \bigg) \\  
&=  [\velocity(\veloargsromy) ]^T \stweightingMatArg{n} \frac{\partial \velocity}{\partial \stateyDiscrete} \frac{\partial \stateyDiscrete}{\partial \genstateyDiscrete} \\
 &=   [\velocity(\veloargsromy) ]^T  \stweightingMatArg{n} \frac{\partial \velocity}{\partial \stateyDiscrete} \basisspace.

@@

 \frac{\partial \minintegrand}{\partial \boldsymbol \genstateyDiscrete} = - \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{n}  \frac{\partial \velocity}{\partial \stateyDiscrete}\basisspace +  [\velocity(\veloargsromy) ]^T \stweightingMatArg{n} \frac{\partial \velocity}{\partial \stateyDiscrete} \basisspace.

@@

\frac{1}{2} \frac{\partial}{\partial \genstateyDiscreteDotArgnt{} }\bigg( \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]  \stweightingMatArg{n}  \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]  \bigg) \\
&= [\genstateyDiscreteDotArgnt{}]^T \basisspace^T \stweightingMatArg{n} \basisspace.

@@

\frac{\partial}{\partial \genstateyDiscreteDotArgnt{}  } \bigg( \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{n} \big[ \velocity(\veloargsromy) \big]  \bigg)\\
 &= \frac{\partial}{\partial \genstateyDiscreteDotArgnt{} } \bigg( [\genstateyDiscreteDotArgnt{}]^T \bigg) \basisspace^T  \stweightingMatArg{n} \big[ \velocity(\veloargsromy) \big] \\ 
 &= \bigg[  \basisspace^T  \stweightingMatArg{n}  \velocity(\veloargsromy )   \bigg]^T \\
 &= [\velocity(\veloargsromy) ]^T \stweightingMatArg{n} \basisspace.

@@

$$\frac{\partial \minintegrand}{\partial \dot{ \genstateyDiscrete} } =   [\genstateyDiscreteDotArgnt{}]^T \basisspace^T \stweightingMatArg{n} \basisspace -  [\velocity(\veloargsromy ) ]^T \stweightingMatArg{n} \basisspace.$$

>>>>

\section{Derivation of the Euler--Lagrange Equations}\label{appendix:eulerlagrange}
This section details the derivation of the Euler Lagrange equations. To this end, we consider the generic functional of the form,
\begin{equation}\label{eq:el_gen}
\mathcal{J}: (\statey,\stateyDot) \mapsto  \int_a^b \integrand(\statey(t),\stateyDot(t),t)  dt,
where $\integrand: \RR{M} \times \RR{M} \times[a,b] \rightarrow  \RRplus$ (for arbitrary $M$) with $\integrand: (\stateyDiscrete,\stateyDotDiscrete,\timeDummy) \mapsto \integrand(\stateyDiscrete,\stateyDotDiscrete,\timeDummy)$. We now introduce the function $\statez: [a,b] \rightarrow \RR{M}$ that is implicitly defined as an extremum of~\eqref{eq:el_gen} subject to the boundary condition $\statez(a) = \statez_a$. 
We introduce an arbitrary function $\variation : [a,b] \rightarrow \RR{M}$ with the boundary condition $\variationArg{a} = \bz$ and define a variation from the extremal by,
\statezBar  &: (\tau,\delta) \mapsto \statez(\tau) + \delta \variation(\tau),\\
&: [a,b] \times \RR{} \rightarrow \RR{M}.
We note that $\statezBar$ satisfies the same boundary condition $\statez$ since $\variationArg{a} = \bz$.
We define a new function that is equivalent to~\eqref{eq:el_gen} evaluated at $\statezBar$ in the first argument and 
$\statezDotBar \equiv d\statezBar / d\timeDummy$ in the second argument,
\mathcal{J}_{\delta}: \delta \mapsto \int_a^b \integrand(\statezBar(t,\delta),\statezDotBar(t,\delta) ,t)  dt.

@@

Using the chain rule,

@@

Noting that

@@

where $\variationDot \equiv d \variation / d\timeDummy$, 
we have

@@

= \int_a^b \bigg[ \frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon),t \big) \variation(t)  + \frac{\partial \integrand}{\partial \stateyDotDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) ,t \big) \variationDot(t) \bigg]dt. $$

@@

%\int_a^b \frac{d}{d\epsilon}\bigg[ \integrand \big(\statezBar(t;\epsilon),\statezDotBar(t;\epsilon),t \big) \bigg] dt 
=  \int_a^b  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) , t \big) \variation(t) - \frac{d}{dt}\bigg( \frac{\partial \integrand}{\partial \stateyDotDiscrete }  \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) ,t \big) \bigg) \variation(t) \bigg]dt + \\ \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statezBar(b,\epsilon),\statezDotBar(b,\epsilon) ,b \big) \variation(b) . 

@@

  \int_a^b  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon),t \big) \variation(t) - \frac{d}{dt}\bigg( \frac{\partial \integrand}{\partial \stateyDotDiscrete }  \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon),t \big) \bigg) \variation(t) \bigg]dt + \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statezBar(b,\epsilon),\statezDotBar(b;\epsilon),b \big) \variation(b)  = 0. 

@@

\section{Evaluation of gradients in the Euler--Lagrange Equations for \methodAcronym\ with \spatialAcronym\ trial subspaces}\label{appendix:vector_calc}
We now derive the specific form of the Euler--Lagrange equations for the \methodAcronym\ formulation with \spatialAcronym\ trial subspaces. Without loss of generality, we present the derivation for a single window $t \in [0,T]$ with a constant basis $\basisspace$ and weighting matrix $\stweightingMat$.  
To obtain the specific form of the Euler--Lagrange equations for the \methodAcronym\ formulation, we need to evaluate the gradients in~\eqref{eq:el1} for the integrand,
\begin{align*}\label{eq:integrand_apx}
 \minintegrand & \vcentcolon
(\genstateyDiscreteArgnt{}, \genstateyDiscreteDotArgnt{} ,\timeDummy) \mapsto \frac{1}{2} \big[
\basisspace \genstateyDiscreteDotArgnt{} - \velocity(\basisspace \genstateyDiscreteArgnt{}
+ \stateIntercept,\timeDummy) \big]^T \stweightingMatArg{} \big[
\basisspace \genstateyDiscreteDotArgnt{}  - \velocity(\basisspace \genstateyDiscreteArgnt{} +
\stateIntercept,t) \big], \\ & 
\vcentcolon \RR{\romdim} \times \RR{\romdim} \times [0,T]
 \rightarrow \RR{} .  
\end{align*}
To evaluate the gradients, we first expand $\minintegrand$:
\begin{align*}
 \minintegrand(\genstateyDiscrete,\genstateyDiscreteDot,\timeDummy)  &= \frac{1}{2} \big[ \basisspace \genstateyDiscreteDotArgnt{}  - \velocity(\basisspace \genstateyDiscreteArgnt{} + \stateIntercept,\timeDummy) \big]^T \stweightingMatArg{} \big[ \basisspace \genstateyDiscreteDotArgnt{} - \velocity(\veloargsromy) \big] \\ 
 &= \frac{1}{2}\big[\basisspace \genstateyDiscreteDotArgnt{}  \big]^T  \stweightingMatArg{}  \big[\basisspace \genstateyDiscreteDotArgnt{} \big]  - \frac{1}{2}\big[ \velocity(\veloargsromy) \big]^T \stweightingMatArg{}  \big[\basisspace \genstateyDiscreteDotArgnt{}\big] - \frac{1}{2} \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{} \big[ \velocity(\veloargsromy) \big]  \\ &+ \frac{1}{2}\big[\velocity(\veloargsromy) \big]^T \stweightingMatArg{} \big[ \velocity(\veloargsromy) \big].
\end{align*}
Since $\stweightingMat$ is symmetric,
\begin{equation}\label{eq:int_expand}
 \minintegrand(\genstateyDiscrete,\genstateyDiscreteDot,\timeDummy)  = \frac{1}{2}\big[\basisspace \genstateyDiscreteDotArgnt{}  \big]^T  \stweightingMatArg{}  \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]  -  \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{} \big[ \velocity(\veloargsromy) \big]  + \frac{1}{2}\big[\velocity(\veloargsromy) \big]^T \stweightingMatArg{} \big[ \velocity(\veloargsromy) \big].
\end{equation}
For notational purposes, we write the above as,
$$  \minintegrand(\genstateyDiscrete,\genstateyDiscreteDot,\timeDummy) =  \minintegrand_1(\genstateyDiscrete,\genstateyDiscreteDot,\timeDummy) +  \minintegrand_2(\genstateyDiscrete,\genstateyDiscreteDot,\timeDummy) +  \minintegrand_3(\genstateyDiscrete,\genstateyDiscreteDot,\timeDummy),$$
where
\begin{align*}
&\minintegrand_1(\genstateyDiscrete,\genstateyDiscreteDot,\timeDummy) \equiv  \frac{1}{2}\big[\basisspace \genstateyDiscreteDotArgnt{}  \big]^T  \stweightingMatArg{}  \big[ \basisspace \genstateyDiscreteDotArgnt{} \big], \\
&   \minintegrand_2(\genstateyDiscrete,\genstateyDiscreteDot,\timeDummy) \equiv   -  \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{} \big[ \velocity(\veloargsromy) \big], \\
&  \minintegrand_3(\genstateyDiscrete,\genstateyDiscreteDot,\timeDummy) \equiv  \frac{1}{2}\big[\velocity(\veloargsromy) \big]^T \stweightingMatArg{} \big[ \velocity(\veloargsromy) \big] . 
\end{align*}
Constructing the Euler--Lagrange equations for this functional $\minintegrand$ requires evaluating the derivatives $\frac{\partial \minintegrand}{\partial \genstateyDiscrete}$ and $\frac{\partial \minintegrand}{\partial \genstateyDiscreteDot}$. We start by evaluating $\frac{\partial \minintegrand}{\partial \genstateyDiscrete}$ and go term by term.

@@

\frac{\partial \minintegrand_2}{\partial \genstateyDiscrete}  &= -\frac{\partial}{\partial \genstateyDiscrete} \bigg( \big[ \basisspace \genstateyDiscreteDot \big]^T \stweightingMatArg{} \big[ \velocity(\veloargsromy) \big] \bigg) \\ 
&= - \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{} \frac{\partial}{\partial \genstateyDiscreteArgnt{}} \bigg( \big[ \velocity(\veloargsromy) \big]  \bigg)\\
 &= -\big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{}   \frac{\partial \velocity}{\partial \stateyDiscrete}\frac{\partial \stateyDiscrete}{\partial \genstateyDiscrete} \\
& = - \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{}  \frac{\partial \velocity}{\partial \stateyDiscrete}\basisspace \\
&= -[\genstateyDiscreteDotArgnt{}]^T \basisspace^T \stweightingMatArg{} \frac{\partial \velocity}{\partial \stateyDiscrete}  \basisspace.

@@

\frac{\partial  \minintegrand_3}{\partial \genstateyDiscrete}  &= \frac{1}{2} \frac{\partial }{\partial \genstateyDiscrete} \bigg( \big[\velocity(\veloargsromy) \big]^T \stweightingMatArg{}\big[ \velocity(\veloargsromy) \big] \bigg) \\  
&=  [\velocity(\veloargsromy) ]^T \stweightingMatArg{} \frac{\partial \velocity}{\partial \stateyDiscrete} \frac{\partial \stateyDiscrete}{\partial \genstateyDiscrete} \\
 &=   [\velocity(\veloargsromy) ]^T  \stweightingMatArg{} \frac{\partial \velocity}{\partial \stateyDiscrete} \basisspace.

@@

 \frac{\partial \minintegrand}{\partial \boldsymbol \genstateyDiscrete} = - \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{}  \frac{\partial \velocity}{\partial \stateyDiscrete}\basisspace +  [\velocity(\veloargsromy) ]^T \stweightingMatArg{} \frac{\partial \velocity}{\partial \stateyDiscrete} \basisspace.

@@

\frac{1}{2} \frac{\partial}{\partial \genstateyDiscreteDotArgnt{} }\bigg( \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]  \stweightingMatArg{}  \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]  \bigg) \\
&= [\genstateyDiscreteDotArgnt{}]^T \basisspace^T \stweightingMatArg{} \basisspace.

@@

\frac{\partial}{\partial \genstateyDiscreteDotArgnt{}  } \bigg( \big[ \basisspace \genstateyDiscreteDotArgnt{} \big]^T \stweightingMatArg{} \big[ \velocity(\veloargsromy) \big]  \bigg)\\
 &= \frac{\partial}{\partial \genstateyDiscreteDotArgnt{} } \bigg( [\genstateyDiscreteDotArgnt{}]^T \bigg) \basisspace^T  \stweightingMatArg{} \big[ \velocity(\veloargsromy) \big] \\ 
 &= \bigg[  \basisspace^T  \stweightingMatArg{}  \velocity(\veloargsromy )   \bigg]^T \\
 &= [\velocity(\veloargsromy) ]^T \stweightingMatArg{} \basisspace.

@@

$$\frac{\partial \minintegrand}{\partial \genstateyDiscreteDot } =   [\genstateyDiscreteDotArgnt{}]^T \basisspace^T \stweightingMatArg{} \basisspace -  [\velocity(\veloargsromy ) ]^T \stweightingMatArg{} \basisspace.$$
